\\LARGE Decision-Optimal Probabilistic Forecast Reconciliation for Expected Shortfall in Hierarchical Time Series

### 2025-08-26 phd_application/phd_propossal.Rmd
update background from Monday feedback

These tail risks are, however, not managed in isolation. Consider a bank's trading book, which consists of multiple portfolios across different desks, where each desk manages various asset classes, and then individual securities. This is an example of a hierarchical structure, with multiple *aggregation levels*. Risk managers need to assess and forecast the risk quantities at several levels, from the overall trading book down to individual securities. Ignoring this naturally-formed hierarchical structure can lead to inconsistent numbers and poor forecasts, resulting in misallocation of capital and suboptimal risk management strategies.

Forecasting such hierarchical time series also arises in many decision-making contexts. From supply chains [@Seaman2022-bb; @Angam2025-od] and energy planning [@Di-Modica2021-ad], to macroeconomic [@El-Gemayel2022-hx; @Li2019-vv] and tourism analysis [@Athanasopoulos2009-lp], stakeholders need forecasts at several aggregation levels to allocate resources and manage risk. These hierarchical structures naturally form *aggregation constraints* (child levels must sum up to parents).

In practice, when forecasts are produced for all series (often called *base forecasts*), they typically violate these aggregation constraints observed in the data; such forecasts are *incoherent* (e.g., security-level numbers don’t sum to the overall trading book). This can undermine downstream decisions that require internal consistency. Forecast reconciliation, a post-processing step, addresses this by adjusting the so-called base forecasts so the final adjusted set is *coherent* with the aggregation structure. Approaches such as OLS [@Hyndman2011-jv], WLS [@Hyndman2016-ic], MinT [@Wickramasuriya2019-xq], and more are developed and commonly used in practice. An additional incentive for the rapid adoption of reconciliation methods is that they improve forecast accuracy [@Athanasopoulos2024-as], with example of the International Monetary Fund reporting improvements in their liquidity forecasts, generating economic benefits via more efficient monetary policy operations [@El-Gemayel2022-hx].

>>>>

These tail risks are, however, not managed in isolation. Consider a hedge fund's investment portfolio returns, which consists returns of different asset classes, and further contains returns of various individual securities. This is an example of a hierarchical structure, with multiple *aggregation levels*. Risk managers need to assess and forecast the risk quantities at several levels, from the overall portfolio, down to individual securities. Ignoring this naturally-formed hierarchical structure can lead to misaligned forecasts, for example, the forecasted returns of individual securities are low while the overall portfolio return is high. This results in misallocation of capital and suboptimal risk management strategies.

Forecasting such hierarchical structure also arises in many other decision-making contexts, from supply chains [@Seaman2022-bb; @Angam2025-od] and energy planning [@Di-Modica2021-ad], to macroeconomic [@El-Gemayel2022-hx; @Li2019-vv] and tourism analysis [@Athanasopoulos2009-lp]. Stakeholders in these settings need forecasts at several aggregation levels to allocate resources and manage risk. These hierarchical structures naturally form *aggregation constraints* (child levels must sum up to parents). Taken together, when we have a collection of time series organised in a hierarchy subject to aggregation constraints, we refer to this as *hierarchical time series*.

In practice, when forecasts are produced for all series (often called *base forecasts*), they typically violate the aggregation constraints observed in the data; such forecasts are *incoherent* (e.g., security-level numbers don’t sum to the overall trading book). This can undermine downstream decisions that require internal consistency. Forecast reconciliation, a post-processing step, addresses this by adjusting the base forecasts so the final adjusted set of forecasts is *coherent* with the aggregation structure. Approaches such as OLS [@Hyndman2011-jv], WLS [@Hyndman2016-ic], MinT [@Wickramasuriya2019-xq], and more are developed and commonly used in practice. An additional incentive for the rapid adoption of reconciliation methods is that they improve forecast accuracy [@Athanasopoulos2024-as]. For instance, the International Monetary Fund reported improvements in their liquidity forecasts, generating economic benefits via more efficient monetary policy operations [@El-Gemayel2022-hx].
